### 2021-05-31 paper/model/number_of_contacts.tex
Update contacts section.

Currently, there are the following contact types:

@@

Theoretically, each contact type can have its own infection probability. However, to
reduce the number of free parameters and thus avoid a potential over-fitting we impose
some constraints. For now, infection probabilities in schools, preschools and nurseries
are equal. Moreover, we restrict all work contacts and all non-work contacts to have
the same infection probability.

>>>>

In our empirical application we distinguish the following types of contacts:

@@

Theoretically, each contact type can have its own infection probability. However, to
reduce the number of free parameters and thus avoid a potential over-fitting we only
estimate different infection probabilities for the areas work, school, preschool and
nurseries, households and other contacts.
